---
title: "Lab 07 - Modelling course evaluations"
author: "Grace Tait"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
#Looking at the distribution of score
ggplot(data = evals, aes(x = score)) +
  geom_histogram(bins = 15) +
  labs(title = "Distribution of score",
       x = "Score",
       y = "Count") 
```

Yes, the distribution is negative skewed. This tells us that the majority of students give courses a higher rating than lower. No this is not what I expected to see. I expected to see a more symmetrical distribution.

From the data visualisation you can see the median is 4.5.

2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
#Looking at the relationship between score and the average beauty of the professor
ggplot(data = evals, aes(x = score, y = bty_avg)) +
  geom_point() +
  geom_jitter()
```


Geom_jitter creates some chaos with the points so we can see more of a trend when points overlap. What was misleading about the initial scatter of points is that it looked very organised and did not look random or have  clear trend.

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
```

```{r tidy-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score_bty_fit)
```

y = 3.88 + 0.07 x 

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit,eval=FALSE}
ggplot(data = evals, aes(x = score,
                                 y = bty_avg)) +
  geom_jitter() +
  geom_smooth(method = "lm")
```

3. Interpret the slope of the linear model in context of the data.

In the data visualisation, you can clearly see that the slope of the linear model is slightly positive which supports the estimate.

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

*Add your interpretation here*

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$___
```

*Add your interpretation here*

6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(___) + ...
```

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
# ... 
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

*Add your narrative here. Use in-line code!*

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

```{r eval = FALSE}
ggplot(___) + ...
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# ...
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
